---
title: "Alexandre Henrique S. Dias"
author: Alexandre Henrique
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
params:
  PDF_EXPORT: FALSE
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- params$PDF_EXPORT

# Holds all the links that are inserted for placement at the end
links <- c()

source('parsing_functions.R') # Functions for building sections from CSV data
source('common_variables.R')  # Small variables for non-csv data such as intro text

# Load csv with position info
position_data <- read_csv('positions.csv')
```

```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> alexandre.hsd@gmail.com
- <i class="fa fa-linkedin-in"></i> [Linkedin](https://www.linkedin.com/in/alexandre-henrique-dias/)
- <i class="fa fa-github"></i> github.com/alexandrehsd
- <i class="fa fa-twitter"></i> alehsdias
- <i class="fa fa-phone"></i> (734) 645-0110

Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
build_skill_bars(skills)
```

Main
================================================================================

Alexandre Henrique S. Dias {#title}
--------------------------------------------------------------------------------

```{r}
cat(sanitize_links(intro_text))
```


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```

Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'research_positions')
```


Industry Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

::: aside
I have worked in a variety of roles ranging from journalist to software engineer to data scientist. I like collaborative environments where I can learn from my peers. 
:::

```{r}
print_section(position_data, 'industry_positions')
```

<br>
<br>
<br>

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

::: aside
I am passionate about education. I believe that no topic is too complex if the teacher is empathetic and willing to think about new methods of approaching task. 
:::

```{r}
print_section(position_data, 'teaching_positions')
```


Selected Data Science Writing {data-icon=chart-line}
--------------------------------------------------------------------------------


::: aside
I regularly blog about data science and visualization on my blog [LiveFreeOrDichotomize.](https://livefreeordichotomize.com/)
:::

```{r}
print_section(position_data, 'data_science_writings')
```



Selected Press (About)  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'about_me_press')
```


<br>
<br>

Selected Press (By)  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'by_me_press')
```




Selected Publications, Posters, and Talks {data-icon=book}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'academic_articles')
```



```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>


")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```


